Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-11-02 tex/scam/appendix.tex
edited up to 8.3

By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. 
Intuitively, we would like to show that the risks of the AC/DC estimators $\hat{f}, \hat{g}$ tends to the risks of the population optimal functions $f^*, g^*$:
\begin{align*}
\| f_0 - \hat{f} \|^2_P & = \| f_0 - f^* \|^2_P + \trm{err}_+(n) \\
\| f_0 - f^* - \hat{g}_k \|^2_P &=  \| f_0 - f^* - g^*_k \|^2_P + \trm{err}_-(n) 
       \quad \trm{for all $k \in S$ where $f^*_k = 0$}
\end{align*}
where the estimation errors $\trm{err}_+(n), \trm{err}_-(n)$ decrease with $n$ at some rate.

>>>>

By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. 
Intuitively, we would like to show that the risk of the AC/DC estimators $\hat{f}, \hat{g}$ tends to the risk of the population optimal functions $f^*, g^*$:
\begin{align*}
\| f_0 - \hat{f} \|^2_P & = \| f_0 - f^* \|^2_P + \trm{err}_+(n) \\
\| f_0 - f^* - \hat{g}_k \|^2_P &=  \| f_0 - f^* - g^*_k \|^2_P + \trm{err}_-(n) 
       \quad \trm{for all $k \in S$ where $f^*_k = 0$},
\end{align*}
where the estimation errors $\trm{err}_+(n)$ and $\trm{err}_-(n)$ decrease with $n$ at some rate.
